---
output:
  md_document:
    variant: markdown_github

---

# Purpose

The aim of this folder is to complete Prac1 of the Data Science of Finance and Economics module.
<br>
In this folder I will create functions in order to:
<ol>
<li> Create a function that loads and saves fmxdat::BRICSTRI in your data folder - saved as a .rds file, with name: BRICS.rds </li>
</ol>
In a different chunk in your README:
<ol start = "2">
<li> Load BRICS.rds, and save this as ‘df_Brics’ in your environment. </li>
<li> Next, create a new chunk where you source a function, ‘filter_df.R’, that does the following: </li>
</ol>
<ol type="a">
<li> filter your dataframe to only consider weekdays between two dates (set by default to 2008 and 2010. </li>
<ul>
<li> Hint. use: rmsfuns::dateconverter and filter the rows using ‘which’. </li>
</ul>
<li> Create and source a function that calculates the simple returns Xlag(X)−1
 for all the columns in your dataframe. </li>
</ol>

Lastly, place this project on github and call it: datsci_Prac1.

### Load in coding scripts

```{r}

rm(list = ls()) # Clean your environment:
gc() # garbage collection - It can be useful to call gc after a large object has been removed, as this may prompt R to return memory to the operating system.
library(pacman)
p_load(tidyverse, rmsfuns)

# Source in all your functions:
list.files('code/', full.names = T, recursive = T) %>% as.list() %>% walk(~source(.))

```


## Data loading

Loading, saving and reading in fmxdat::BRICSTRI data file 

```{r}
load_save_data_func(package_name = "fmxdat", data_name = "BRICSTRI", file_name = "dat_BRICSTRI")
df_Brics <- read_rds(file = "data/dat_BRICSTRI.rds")

```

## Filtering Data

Filtering out all weekdays between 2008 and 2010.

```{r}
filter_df <- filter_func(dat = df_Brics, start_date = as.Date("2008-01-01"), end_date = as.Date("2010-12-31"))
```

## Calculating Returns

Calculate simple return in the form $`\frac{X}{lagX} - 1`$.

```{r}
ret_df <- ret_calc(dat = filter_df)
head(ret_df)
```


